---
title: "WeatherApp"
author: "Justin Thompson"
date: "6/1/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(leaflet, quietly = TRUE)
require(shiny, quietly = TRUE)
require(tidyverse, quietly = TRUE)
require(httr, quietly = TRUE)
require(jsonlite, quietly = TRUE)
require(lubridate, quietly = TRUE)
require(plotly, quietly = TRUE)
require(geosphere, quietly = TRUE)
require(mapview, quietly = TRUE)
require(kableExtra, quietly=TRUE)
source('./weatherFunctions.R')
```

# Shiny Map
Here's a short example of using advanced `shiny` features along with `leaflet` and external data building using an API to create an app which displays the weather information of a location we select. We'll step through the app build, adding content and modifying the layers as we add complexity.

## Lesson 1
Let's create a basic page with a map. We'll use the `leaflet` package to generate the map for us, they make great maps and its easy to use. Lets get started.

### The parts of shiny file
There are three parts (or code blocks) of a Shiny file:

1. Setup
2. User Interface (UI)
3. Server

#### Setup
Things you want all objects and processes to access.

* Packages
* External functions
* Data pre-processing scripts
* Global data

To start our app we need the packages `shiny` and `leaflet`. We'll add other objects as we go along.

```{r, eval=FALSE}
require(leaflet, quietly = TRUE)
require(shiny, quietly = TRUE)
require(tidyverse, quietly = TRUE)
```

#### UI

* Data object, generates a very large list full of things
* Creates the externals (or front end) of the webpage
* Many options and settings
* Syntax is not intuitive for first time users

We'll begin with a simple page. First we call the `fluidPage` function. This page-type gives us nice control over objects within the page and the page will re-size itself and do some work in rearranging things for us. To start with we only add an output slot for a leaflet plot. We'll link to that slot using the `server`.

```{r}
ui <- fluidPage(
  leafletOutput('mymap')
)
```

Look at the `ui` object, our `fluidPage` function call created the shell of a webpage!

```{r}
#unlist(ui)
print(ui[[3]][[1]])
```

#### Server

* Function that does the work (or back end)
* Generates output, sends to UI for display
* Tricky syntax
  + Everything is a sub function
  + Watch out for object scoping issues

Server is a function that runs the back end of the webpage. It does the work and passes data to the UI for display. Basically the server is the brains of the operation, it controls what is displayed by the UI. Whereas the UI is a large function call with a difficult syntax, the server syntax is more akin to standard coding where you go top to bottom, line by line just like a normal script. The trick is keeping track of object scoping. If you create an object at one point of the server it may not be available to other commands depending on how its written.

For our app we'll create a `leaflet` plot at full zoom (level = 1) centered on Kansas. The `renderLeaflet` function takes the plot generated by the enclosed `leaflet` syntax and renders it into an object the UI will understand. The server sends that object to the appropriate slot in the UI using the `output` list.

```{r}
server <- function(input, output, session){
  output$mymap <- renderLeaflet({
    leaflet() %>% 
      addTiles() %>% 
      setView(-98.5795, 39.8283, zoom=1)
  })
}
```

#### Put it together

Now to put it together and create a webpage. The basic method is call the `shinyApp` function and put it all together. This opens a web browser and displays the page.

```{r}
shinyApp(ui, server)
```

Now we have a simple webpage. All it does is show a `leaflet` plot with the settings we give it. But since javascript powers `leaflet` plots we get a ton of functionality. Here all we can do is zoom in and out but later we'll use some of the other features.

## Lesson 2

There are a few ways we could select the location to get the weather, but to be as interactive as possible we'll let the user click on the map and use that click to pick the location. Much more interesting than typing in a zip code or lat-long.

### UI

First we'll modify our UI to give us a display slot for the lat-long. This helps in debugging, we want to make sure the mechanics of getting the information works before attaching other complicated processes.

```{r}
ui <- fluidPage(
  leafletOutput('mymap', width=800, height=350),
  textOutput('latlon'),
  p()
)
```
We added a simple text output for the UI to display the information the server gets for us.

### Server

Now modify the server to get the information. This is more complicated, it requires a knowledge of reactivity in `shiny` and how `leaflet` works. A mouse click on the map creates an object with the latitude, longitude of the location clicked along with additional information about the layers if there are any. We can access that information by capturing the information in the `event` object. We use `observe` to watch for that specific action and send the text to the UI using the `renderText` function. The `isolate` function prevents creating a reactive object when we render the text.

```{r}
server <- function(input, output, session){
  output$mymap <- renderLeaflet({
    leaflet() %>% 
      addTiles() %>% 
      setView(-98.5795, 39.8283, zoom=3)
  })
  observe({
    event <- input$mymap_click
    if (is.null(event)){
      return()
    }
    isolate({
      output$latlon <- renderText(paste0('Latitute=',event$lat,', Longitude=',event$lng))
    })
  })
}
```

### Apply the changes

```{r}
shinyApp(ui, server, options=list(height=600))
```

Click somewhere, the Latitude and Longitude of that location should appear each time you click. We'll remove this text later, but we know we have a working map.

## Lesson 3

Now we get technical. We'll get the locations of all of the weather stations in the US and plot each location on the map. We'll use the National Weather Services' (NWS) API along with custom functions in the `weatherFunctions` file. You can find the API documentation [here] (https://www.weather.gov/documentation/services-web-api). Using the map-click information and the API we'll then get and plot the temperature forecast for the closest weather station.

### Setup

We're going to change our Setup block to include some data at rest and a file with the external functions we need to get our information (Note these functions require an active internet connection). First, we add additional packages required to make the API work and read in the function file using `source` (make sure the file is in your working directory.

```{r, eval=FALSE}
require(leaflet, quietly = TRUE)
require(shiny, quietly = TRUE)
require(tidyverse, quietly = TRUE)
require(httr, quietly = TRUE)
require(jsonlite, quietly = TRUE)
require(lubridate, quietly = TRUE)
source('./weatherFunctions.R')
```

Next we'll build our weather station data using the `getWeatherGeo()` function.

```{r}
stationTib <- getWeatherGeo()
```

Now we have information on each of the ~2500 NWS weather stations, including the latitude and longitude.

### UI

We've changed from a `fluidPage` to a `bootstrapPage` to allow inclusion of CSS tags in the page. This gives greater control over how the page displays. We also add an output slot for the forecast plot.

```{r}
ui <- bootstrapPage(
  tags$style(type = 'text/css', 'html, body {width:100%;height:100%;cursor: crosshair}'),
  leafletOutput('mymap', width='100%', height='100%'),
  plotOutput('forecastPlot')
)
```

### Server

The server will get more and more complicated, as is standard when making a `shiny` app. Remember, the server is the brains.

We replaced the basic map background with a nice-looking template from "Mapbox" (always remember to give attribution). We also added data to our map with markers for the weather stations. To help the user we put the station identifier as the pop-up label.

In the `observe` function we added a function call to the `getWeatherForcast` function. This call uses the latitude and longitude stored from the map click as inputs, sends the info to the API to get the weather data, and returns a `ggplot` object of the forecast.

```{r}
server <- function(input, output, session){
  output$mymap <- renderLeaflet({
    leaflet(data=stationTib) %>% 
      addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
               attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>% 
      addCircleMarkers(lng = ~ lon,
                       lat = ~ lat,
                       label = ~ paste0('Station: ', stationIdentifier),
                       labelOptions = labelOptions(textOnly = FALSE),
                       radius = 3,
                       color = 'green',
                       stroke=FALSE,
                       fillOpacity = 0.7) %>% 
      setView(-98.5795, 39.8283, zoom=3)
  })
  observe({
    event <- input$mymap_click
    if (is.null(event)){
      return()
    }
    isolate({
      m <- getWeatherForcast(event$lat,event$lng)
      output$forecastPlot <- renderPlot({m})
    })
  })
}
```

### Apply the changes

```{r}
shinyApp(ui, server, options=list(height=600))
```

Now when you click the map a new chart appears with the forecast for that area (API errors may occur, try clicking somewhere else if this happens to you). You may need to scroll down in the map panel, the forecast plot may be below the map.

## Lesson 4

Next we'll add some additional features and change the display to make it more eye-catching. We'll add a chart to get the historical observations of the closest weather station and add an opaque panel on the right side of the page where we'll place our charts.

### Setup

The only change to the setup is the addition of the `geosphere` package to help us find the closest weather station to a clicked location.
```{r, eval=FALSE}
require(leaflet, quietly = TRUE)
require(shiny, quietly = TRUE)
require(tidyverse, quietly = TRUE)
require(httr, quietly = TRUE)
require(jsonlite, quietly = TRUE)
require(lubridate, quietly = TRUE)
require(geosphere, quietly = TRUE)
source('./weatherFunctions.R')

stationTib <- getWeatherGeo()
```

### UI
Big changes to the UI. We've added a new function call to our `bootstrapPage` called `absolutePanel`. This panel is "pinned" in place on the page so its position appears absolute regardless of how the page is re-sized. This function has a lot of settings we can adjust. This panel is pinned on the top-right corner (to start) and automatically adjusts the left and bottom positions. The user can drag the panel around the screen as desired, but this un-pins to panel.

The `plotOutput` display slots are moved to the panel also. Depending on you machine's display setting you may need to play with the dimensions of the plots to give it the best look (always a struggle).
```{r}
ui <- bootstrapPage( # change from fluidPage to bootstrap to add css tags
  tags$style(type = 'text/css', 'html, body {width:100%;height:100%;cursor: crosshair}'),
  leafletOutput('mymap', width='100%', height='100%'),
  absolutePanel(id = 'plots', class = 'panel panel-default', fixed = TRUE,
                draggable = TRUE, top = 60, left = 'auto', right = 20, bottom = 'auto',
                width = 280, height = 'auto', style = 'opacity: 0.8',
                
                h3(' Quick Plots'),
                
                plotOutput("forecastPlot", height = 200),
                plotOutput("observationPlot", height = 200)
  )
)
```

### Server
The only change to the server is the addition of a function call to get the recent observations of the closest weather station, `getRecentObservations`.
```{r}
server <- function(input, output, session){
  

  output$mymap <- renderLeaflet({
    leaflet(data=stationTib) %>% 
      addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
               attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>% 
      addCircleMarkers(lng = ~ lon,
                       lat = ~ lat,
                       label = ~paste0('station:', stationIdentifier),
                       labelOptions = labelOptions(textOnly = FALSE),
                       radius = 3,
                       color = 'green',
                       stroke=FALSE,
                       fillOpacity = 0.7) %>%
      addLegend('bottomleft',
                colors='green',
                labels='Stations') %>% 
      setView(-98.5795, 39.8283, zoom=3)
  })
  observe({
    event <- input$mymap_click
    if (is.null(event)){
      return()
    }
    isolate({
      forPlot <- getWeatherForcast(event$lat,event$lng)
      output$forecastPlot <- renderPlot({forPlot})
      obPlot <- getRecentObservations(event$lat,event$lng)
      output$observationPlot <- renderPlot({obPlot})
    })
  })
}
```
### Apply the changes

```{r}
shinyApp(ui, server, options=list(height=600))
```
When the page loads you'll see an opaque white box on the right. That's the absolute panel. Now when you click the map a new chart appears with the forecast for that area and a plot for the recent observations of the nearest station. Both of these plots appear in the panel.

## Lesson 5
We change the page type again to allow for more features. We also add user controls to the observations plot and add a data table showing the recent observations on another page.

### Setup
No change here. That was easy.

### UI
We've changed the page type again, this time we're using a `navbarPage` so we can create different tabs across the top to display different information. We send information to each tab using the `tabPage` function and put the code for each page inside that function. In the map page's code we include a function `fillPage` which forces the map to always fill the available area of the browser window. At the bottom of the absolute panel we add a date range slider to control the dates of the plotted observations along with a "redraw" button. The `fluidRow` and `column` functions format the controls' locations.

In the second tab panel we simply add a slot to display a table.
```{r}
ui <- navbarPage(title='Weather Map',
  tabPanel('Maps',
    fillPage(
      tags$style(type = "text/css", "#mymap {height: calc(100vh - 80px) !important;cursor: crosshair}"),
    leafletOutput('mymap', width='100%', height='100%')),
    absolutePanel(id = 'plots', class = 'panel panel-default', fixed = TRUE,
                  draggable = TRUE, top = 60, left = 'auto', right = 20, bottom = 'auto',
                  width = 280, height = "auto", style = 'opacity: 0.8',
                  
                  h3('Quick Plots'),
                  
                  plotOutput('forecastPlot', height = 200),
                  plotOutput('observationPlot', height = 200),
                  fluidRow(
                    column(
                      12, align='center',
                      sliderInput('dateSlider',
                                  'Plot Range',
                                  min=today()-30,
                                  max=today(),
                                  value=c(today()-14, today()),
                                  step = 1,
                                  timeFormat = "%Y-%m-%d",
                                  width='80%'),
                    )
                  ),
                  fluidRow(
                    column(
                      12, align='center',
                      actionButton('redrawPlot','Redraw')
                    )
                  )
    ),
  ),
  tabPanel('Observation Explorer',
           tags$style(type = "text/css", "html, body {overflow-y:scroll}"),
           tableOutput('dataOut')
  )
)

```

### Server
In the server we first add a message box telling the user the API is running and not to be impatient. Next we modify the server to allow for redrawing the the observation plot without having to rerun the API. We move the observation object outside of the `isolate` function which changes it's scope, we want to access that information whenever we want to redraw the observations plot. We add a data table render and send the information to the correct slot on the data tab. Finally, we tie the "redraw" button to a redraw event which filters the observation data based on the dates on the date range slider.
```{r}
server <- function(input, output, session){
  output$mymap <- renderLeaflet({
    leaflet(data=stationTib) %>% 
      addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
               attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>% 
      addCircleMarkers(lng = ~ lon,
                       lat = ~ lat,
                       label = ~paste0('station:', stationIdentifier),
                       labelOptions = labelOptions(textOnly = FALSE),
                       radius = 3,
                       color = 'green',
                       stroke=FALSE,
                       fillOpacity = 0.7) %>%
      addLegend('bottomleft',
                colors='green',
                labels='Stations') %>% 
      setView(-98.5795, 39.8283, zoom=3)
  })
  obPlot <- reactiveValues()
  observe({
    event <- input$mymap_click
    if (is.null(event)){
      return()
    }
    showModal(modalDialog(
      title = 'Connecting',
      'Waiting for API response'
    ))
    obPlot$p <- getRecentObservations(event$lat,event$lng)
    isolate({
      forPlot <- getWeatherForcast(event$lat,event$lng)
      output$forecastPlot <- renderPlot({forPlot})
      output$observationPlot <- renderPlot({obPlot$p$plot})
      output$dataOut <- renderTable(obPlot$p$obs)
    })
    removeModal()
  })
  observeEvent(input$redrawPlot, {
    # redraw button clicked
      newPlot <- plotRecentObservations(obPlot$p$obs, obPlot$p$station,
                                        input$dateSlider[1], input$dateSlider[2])
      output$observationPlot <- renderPlot({newPlot})
    })
}

```
### Apply the changes

```{r}
shinyApp(ui, server, options=list(height=600))
```
When the page loads you'll see two tabs on top and the range slider with button in the panel. The charts appear as they did before, but now you can adjust the date range of the observation display. Also, the data tab fills with the table of all available observations for that weather station.

## Lesson 6
Our final iteration (feel free to do your own modifications though). Here we modify the display so that the panel is not visible when the page loads, it only appears when the user clicks a location. And we give the user a button to close the panel. We also change the library used to create the plots to introduce the functionality of `plotly`.

### Setup
Add the `plotly` and `leafem` libraries.
```{r, eval=FALSE}
require(leaflet)
require(shiny)
require(tidyverse)
require(httr)
require(jsonlite)
require(lubridate)
require(plotly)
require(geosphere)
require(leafem)
source('./weatherFunctions.R')
stationTib <- getWeatherGeo()
```

### UI
The UI looks much smaller and simpler now. The absolute panel is gone, now we only have the tab definitions and output slots. We add a tag (HTML code placeholder) for where we'll put the panel later.
```{r}
ui <- navbarPage(title='Weather Map',
  # page one
  tabPanel('Maps',
    fillPage(
      tags$style(type = 'text/css', '#mymap {height: calc(100vh - 80px) !important;cursor: crosshair}'),
      leafletOutput('mymap', width='100%', height='100%')),
  tags$div(id='chartUI') # placeholder for the UI
  ),
  # page two
  tabPanel('Observation Explorer',
           tags$style(type = 'text/css', 'html, body {overflow-y:scroll}'),
           tableOutput('dataOut')
  )
)
```

### Server
The server is now very complicated. As it should be, its the brain after all. When you look closely, however, we just moved the absolute panel information down into the server. We use `insertUI` to create the absolute panel and place it into the placeholder tag we created in the UI. Notice the `id` of the panel, we use that as a reference to also `removeUI` on button click or when the user clicks a new location without removing the panel first.

We also change the plot render function from `renderPlot` to `renderPlotly`. The `plotly` functions use javascript and have many nice features we can take advantage of like mouse-over text, in panel zoom, and a print feature. Just for fun, we add `addMouseCoordinates` to the `leaflet` map to give the coordinates of the current mouse position in the upper left corner. This requires the `leafem` package.
```{r}
server <- function(input, output, session){
  # generate the initial plot with all the stations
  output$mymap <- renderLeaflet({
    leaflet(data=stationTib) %>% 
      addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
               attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>% 
      addCircleMarkers(lng = ~ lon,
                       lat = ~ lat,
                       label = ~paste0('station:', stationIdentifier),
                       #label = ~(hoverText),
                       labelOptions = labelOptions(textOnly = FALSE),
                       radius = 3,
                       color = 'green',
                       stroke=FALSE,
                       fillOpacity = 0.7) %>%
      addLegend('bottomleft',
                colors='green',
                labels='Stations') %>% 
      leafem::addMouseCoordinates() %>% 
      setView(-98.5795, 39.8283, zoom=3)
  })
  # placeholder for the reactive object created later
  # this is one method to use objects created inside of an observe function outside of the function
  obPlot <- reactiveValues()
  # when the event fires (here when the map is clicked) do things
  observe({
    event <- input$mymap_click
    # if the event is empty, quit
    if (is.null(event)){
      return()
    }
    # remove the UI if its present
    removeUI(selector = '#subPanel')
    # popup message
    showModal(modalDialog(
      title = 'Connecting',
      'Waiting for API response'
    ))
    # create the panel for the charts when the map is clicked
    insertUI(
      selector = '#chartUI', # send it to the placeholder tags 
      # standard inputs for the panel
      ui = tags$div(
        id='subPanel',
        absolutePanel(
          id = 'plots', class = 'panel panel-default',
          fixed = TRUE, draggable = TRUE, top = 60,
          left = 'auto', right = 20, bottom = 'auto',
          width = 280, height = 'auto', style = 'opacity: 0.8',
          h3('Quick Plots'),
          plotlyOutput('forecastPlot', height = 200),
          plotlyOutput('observationPlot', height = 200),
          fluidRow(
            column(
              12, align='center',
              sliderInput(
                'dateSlider',
                'Plot Range',
                min=today()-30,
                max=today(),
                value=c(today()-14, today()),
                step = 1,
                timeFormat = "%Y-%m-%d",
                width='80%'),
              )
            ),
          fluidRow(
            column(
              6, align='center',
              actionButton('redrawPlot','Redraw')
              ),
            column(
              6, align='center',
              actionButton('closePanel', 'Close')
              )
            )
          )
        ),
    )
    # create the reactive object for recent observations using external function
    obPlot$p <- getRecentObservations(event$lat,event$lng)
    # the things in isolate are not reactive, do not change
    isolate({
      # get the forcast and observations and plot
      forPlot <- getWeatherForcast(event$lat,event$lng)
      output$forecastPlot <- renderPlotly({forPlot})
      output$observationPlot <- renderPlotly({obPlot$p$plot})
      output$dataOut <- renderTable(obPlot$p$obs)
    })
    removeModal()
  })
  observeEvent(
    input$redrawPlot, {
    # redraw button clicked
    # does not rerun the data pull function, uses the reactive object
      newPlot <- plotRecentObservations(
        obPlot$p$obs,
        obPlot$p$station,
        input$dateSlider[1],
        input$dateSlider[2])
      output$observationPlot <- renderPlotly({newPlot})
    })
  # remove the panel if the user clicks
  observeEvent(
    input$closePanel, 
    removeUI(
      selector = '#subPanel'
      )
    )
}
```

### Apply the changes

```{r}
shinyApp(ui, server, options=list(height=600))
```
When the page loads you'll see just the map with two tabs on top. The charts appear inside the panel after a click on the map as they did before. Mouse-over the charts, notice the difference? The display area for these charts is a little small, but you see their capabilities.

## Summary

We created a shiny app from scratch, going from a very basic app to a very complicated app by the end. This method of slowly adding capabilities is a great way to build your skills and get comfortable with the program. Keys to success:

* Do your analysis first, then make the app.
* Keep analysis code in outside functions and scripts and use shiny to access them.
* Have a well-thought-out design first, then start creating the app.
* Debug, debug, debug, then deploy.


---

## API Function Description

<hr style="height:2px;border-width:0;color:red;background-color:gray">
<center><font size="4">getWeatherGeo() &emsp; &emsp; &emsp; *get the geospatial information for the weather stations*</font></center>
<hr style="height:2px;border-width:0;color:red;background-color:gray">

**Description**

|    Get the admin information of all current NWS weather stations. Information includes:
* Latitude and longitude
* Elevation and elevation units
* Timezone
* Station name and four-letter identifier
&nbsp;

**Usage**

|    getWeatherGeo()
&nbsp;

**Arguments**

|    None
&nbsp;

**Value**

|    A tibble with 10 columns containing the stations' admin information.
&nbsp;

**Examples**
stationLoc = getWeatherGeo()
&nbsp;

<hr style="height:2px;border-width:0;color:red;background-color:gray">
<center><font size="4">getRecentObservations() &emsp; &emsp; &emsp; *get the recent temperature observations of a weather station*</font></center>
<hr style="height:2px;border-width:0;color:red;background-color:gray">

**Description**

|    Get the historical weather observations of a particular weather station. Observations are currenly limited to temperature.
&nbsp;

**Usage**

|    getRecentObservations(lat, lon, startDate=0, endDate=0)
&nbsp;

**Arguments**

```{r, echo=F}
text_tbl <- data.frame(
  Argument = c('lat', 'lon', 'startDate', 'endDate'),
  Description = c('The latitude of the weather station.(dbl)',
                  'The longitude of the weather station.(dbl)',
                  'The date of the earliest observation to view. (Date)',
                  'The date of the latest observation to view. (Date)')
)

kable(text_tbl) %>%
  kable_styling(bootstrap_options = "striped", font_size = 12) %>% 
  row_spec(0, bold=TRUE, font_size = 16)
```

**Value**

|    A list containing a plot object of the observations within the time limits and a tibble containing a table of the observations at 20 minute incriments.
&nbsp;

**Examples**

lat <- 38.8894

lon <- -77.0352

stationLoc = getRecentObservations(lat, lon, startDate=as.Date('2020-06-01'), endDate=as.Date('2020-06-03'))

<hr style="height:2px;border-width:0;color:red;background-color:gray">
<center><font size="4">getWeatherForcast() &emsp; &emsp; &emsp; *get the 7 day weather forecast for a given location*</font></center>
<hr style="height:2px;border-width:0;color:red;background-color:gray">

**Description**

|    Get the weather forecast for the next 7 days. Forecast is currently limited to temperature.
&nbsp;

**Usage**

|    getWeatherForcast(lat, lon)
&nbsp;

**Arguments**

```{r, echo=F}
text_tbl <- data.frame(
  Argument = c('lat', 'lon'),
  Description = c('The latitude of the weather station.(dbl)',
                  'The longitude of the weather station.(dbl)')
)

kable(text_tbl) %>%
  kable_styling(bootstrap_options = "striped", font_size = 12) %>% 
  row_spec(0, bold=TRUE, font_size = 16)
```

**Value**

|    A plot object with current weather forecast.
&nbsp;

**Examples**

lat <- 38.8894

lon <- -77.0352

p = getWeatherForcast(lat, lon)

<hr style="height:2px;border-width:0;color:red;background-color:gray">
<center><font size="4">plotRecentObservations() &emsp; &emsp; &emsp; *plot the recent observations (internal use)*</font></center>
<hr style="height:2px;border-width:0;color:red;background-color:gray">

**Description**

|    Create a plot object using the data returned from an API request. For internal use.
&nbsp;

**Usage**

|    plotRecentObservations(obsTib, station, startDate, endDate){
&nbsp;

**Arguments**

```{r, echo=F}
text_tbl <- data.frame(
  Argument = c('obsTib', 'station', 'startDate', 'endDate'),
  Description = c('Tibble containing the observations from the API',
                  'The station name',
                  'The date of the earliest observation to view. (Date)',
                  'The date of the latest observation to view. (Date)')
)

kable(text_tbl) %>%
  kable_styling(bootstrap_options = "striped", font_size = 12) %>% 
  row_spec(0, bold=TRUE, font_size = 16)
```

**Value**

|    A plot object of the recent observations.
